\documentclass{article}
%-----------------------------------------------------------
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\textheight=11.3in 
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=10in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{Abhishek Aryan} \hskip 4.1in Email-id : \textbf{aaryan@iitk.ac.in} \\
\indent Mathematics and Scientific Computing \hskip 3.05in Mobile No.: \textbf{7318018967}\\
\indent Indian Institute of Technology Kanpur  \hskip 3in Alt Mob No.: \textbf{7727098585}\\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\ [-0.5cm]
%\begin{itemize}
\begin{table}[ht!]
\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in}}
\hline
\textbf{Examination} & \textbf{Institute/School} & \textbf{Year} & \textbf{CPI/\%/AIR} \\
\hline
Under Graduation & IIT Kanpur & (ongoing) & 7.2 \\
10th & Maharaja Sawai Man Singh Vidyalaya, Jaipur & 2014 & 10\\
12th & Maharaja Sawai Man Singh Vidyalaya, Jaipur & 2016 & 91\%\\
JEE Advanced & \hskip 1.4in - & 2016 & AIR-683\\
\hline
\end{tabular}
\end{center}
\end{table}
%\end{itemize}
\\ \\ [-1cm]

\resheading{\textbf{PROJECTS} }\\[\lsep]
\begin{itemize}
\item \textbf{Portfolio Optmization and Kolmogorov Complexity} \textit{(Reading Project)}\hskip 3.5cm\textit{May 2017 - Present} \\
 \emph{Prof. Satyadev Nandakumar CSE Department.} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Rediscovered details of proofs from [A Sandwich Proof of the Shannon-McMillan-BreimanTheorem.] (http://www-isl.stanford.edu/~cover/papers/paper83.pdf) 
	\item Understood algorithms from Asymptotic Optimality and Asymptotic Equipartition Properties of Log-Optimum Investment (isl.stanford.edu/~cover/papers/paper82.pdf) to use in complexity theory
\end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{Studying PLM Instutionalization using Structural Equation Modelling } \hskip 3cm\textit{Aug'17 - April'18}\\
 \emph{Mentor: Mrs. Shikha Singh (PhD Student) IME Department} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective: To establish the use of Product Life Cycle Management in the Indian market and to present the various factors that are critical to the institutionalization of it.
	\item Read and understood the Structural equation Modelling technique from Kline: Principles and Practices of Structural Equation Modeling. 
	\item Analyzed the data to test the model using various statistical methods such as SEM, Multiple Linear regression, Factor Analysis etc. using R and thereby ascertain the critical factors.
\end{itemize}
\end{itemize}
%\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \indent\textbf{Languages} (C++,Matlab)
      \indent\textbf{Script} (Python, R), 
      \indent\textbf{Tools} (\LaTeX, Rstudio, Git, MS-Excel).
\end{itemize}

\resheading{\textbf{RELEVANT COURSES} }\\[\lsep]
\begin{itemize}
\item \indent\textbf{Statistics} (MSO201:Introduction to Statistics, MTH412: Applied Stochastic Processes*)
      \indent\textbf{Management} (MBA665: Manufacturing Planning and Control)
      \indent\textbf{Computer Science} (Data Structures and Algorithms*)
      \newline (* ongoing courses)
\end{itemize}

\resheading{\textbf{POSITION Of RESPONSIBILITY HELD} }\\[\lsep]
\begin{itemize}
\item \noindent Senator BT-BS Y16 \hskip 11.8cm \textit{Sept'16-Mar'17} \\[-0.6cm]
  	\begin{itemize}\itemsep \isep
  	\item Elected to represent a batch of more than 800 freshman students in the Students' Senate which is the highest legislative body of the Students' Gymkhana. 
  	\end{itemize}
\item \noindent Secretary, Students' Senate \hskip 10.5cm \textit{July'17-Mar'18} \\[-0.6cm]
    \begin{itemize}\itemsep \isep
  	\item Assist the Chairperson, Students' Senate in carrying out his duties to the Students' Senate and various institute forums and maintain the office of the Senate.
  	\end{itemize}
\item \noindent Finance Convener, Students' Senate (Acting)\hskip 7.9cm \textit{May'18-July'18} \\[-0.6cm]
     \begin{itemize}\itemsep \isep
  	\item Convener of the Finance Committee, responsible for framing the financial policies and all supervising all financial matters of the Gymkhana.
  	\end{itemize}
\item \noindent Students' Senate Nominee, SUGC (Acting) \hskip 8cm \textit{May'18-July'18} \\[-0.6cm]
     \begin{itemize}\itemsep \isep
  	\item Member of the Standing Committee of the Academic Senate responsible for framing the various academic policies and reforms for the UG students.
  	\item Handled the cases of appeal against termination of academic program of 86 students. 
  	\end{itemize}
\item \noindent Company Coordinator at Students’ Placement Office \hskip 6.6cm \textit{Aug'17-Jan'18}
\end{itemize}

\resheading{\textbf{EXTRA CURRICULAR and WORK EXPERIENCE} }\\[\lsep]
\begin{itemize}
\item \noindent TGELF Leadership and Life Skills Program from 2012-2014
\item \noindent Volunteer at Studnts' Placemnt office during Placement 2016 drive.
\end{itemize}

\end{document}

